Measuring precise radial velocities and cross-correlation function line-profile variations using a Skew Normal density

### 2018-05-29 manuscript.tex
reviewing sect 4 in process

%-----------------------------------------------------------------------------------------------------------------------------------------------
\section{Simulation Study} \label{sec:soap}
In order to evaluate the performance of the proposed SN approach for modelling the CCF and the benefit of using the proposed correction for stellar activity (See Eq.~\ref{eq:RV:correction}), we begin by considering a simulation study using spectra generated from the Spot Oscillation And Planet (SOAP) 2.0 code \citep{Dumusque-2014b}.

\umberto{Add more information on SOAP, the way we retrieve the CCFs with SOAP, the characteristics of the CCF (i.e. how many points, ...) and the reasons why we need CCFs simulated with SOAP.}
\umberto{Specify characteristic of the star.}
\xavier{}

@@

\umberto{Specify characteristic of the faculae.}\xavier{}

Fig.~\ref{fig:faculae} shows the results obtained when a faculae is present on the photosphere of the star. It is possible to note that, although there is not a planet, the presence of the faculae leads to spurious variations in RV's for all the proposed indicators. SN mean RV seems to have the smallest spurious variations caused by the faculae.

>>>>

%-----------------------------------------------------------------------------------------------------------------------------------------------
\section{Simulation Study} \label{sec:soap}
In order to evaluate the performance of the proposed SN approach for modelling the CCF and the benefit of using the proposed correction for stellar activity (See Eq.~\ref{eq:RV:correction}), we begin by considering a simulation study using spectra generated from the Spot Oscillation And Planet 2.0 code \citep[SOAP 2.0,][]{Dumusque-2014b}.

\xavier{For a given configuration of spots and faculae on the stellar surface, SOAP 2.0 gives as output the simulated CCF as a function of rotational phase. The code returns as well the RV and the FWHM by fitting a Normal density to the CCF, and the BIS SPAN by calculating the bisector of the CCF. SOAP 2.0 gives us therefore noiseless CCFs affected by stellar activity, which will be used to compare the benefits of fitting a SN density to the CCF compared to a Normal density fit.}

\xavier{For the simulations shown below, we modelled a star similar to the Sun. The stellar rotational period is set to 25.0 days, the radius to a solar radius and the star is seen equator on. The stellar effective temperature is set to 5778 K (NASA Planetary Fact Sheets), and we use a quadratic limb-darkening relation with linear and quadratic coefficients 0.29 and 0.34, respectively \citep[][]{Oshagh-2013a, Claret-2011}. In addition, to be able to compare the result of those simulations with real data obtained with the HARPS spectrograph in Sect.~\ref{sec:4}, we asked SOAP 2.0 to generate CCFs of width 40 \kms and of resolution 115'000, so that those CCFs would have the same properties as the one returned by the HARPS data reduction.}

@@

\xavier{Fig.~\ref{fig:faculae} shows the barycentric variation of the CCF induced by a simulated equatorial faculae of size 3\% relative to the visible stellar hemisphere. We compare the barycentric variation as measured when fitting a Normal density and taking its mean (RV), and when fitting a SN density and taking its mean (SN mean RV) or its median (SN median RV). Although the different estimates for the RV present similar variation as a function of rotational phase, we note that SN mean RV present a smaller amplitude than the two others.}
